---
title: 'Animal Crossing Stuff'
author: 'Kaleb Cervantes'
date: '`r Sys.Date()`'
output:
  html_document:
    number_sections: true
    toc: true
---

I like to use a lot of `tidyverse` stuff so this may be a good thing to load.
```{r, results = "hide"}
library(tidyverse) # metapackage of all tidyverse packages
```

I played a lot of *Animal Crossing: New Horizons* since April 2020 so I thought it might be fun to look through some data for the game.

# K.K. Slider's Funtime Collection
I managed to successfully collect all of the K.K. Slider songs (twice since I collected all before and after the 2021 update).
I thought it would be interesting to analyze some of the data on these songs
```{r}
kk <- read_csv("../input/animal-crossing-new-horizons-nookplaza-dataset/music.csv")
head(kk)
```

Here we can see that most of the columns are stored as the `chr` type. This makes sense for most of the columns but there are some where it may be beneficial to change.

* `Buy`: This is the buying price for the song in bells.
This seems to be stored as a `chr` because there is a `NFS` value in the dataset to denote songs that you are unable to buy.
It may be beneficial to replace these values with `NA`.

* `Size`: This denotes the size of the object when placed down. It may help to store this as a tuple of integers.

All of the other variables are stored as `dbl`. This does not make as much sense for `Sell`, which denotes the selling price in bells.
In the game, bell price is treated as an integer, so it may be beneficial to change this to an integer type.